---
title: "Beer Case Study"
author: "Ikenna Nwaogu"
date: "11/13/2019"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This R Markdown document is made interactive using Shiny. Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r eruptions, echo=FALSE}

library(shiny)
library(dplyr)
library(plyr)
library(ggplot2)


```

```{r echo = FALSE}
# read in data
beers = read.csv('./data/Beers.csv', header = TRUE) # Import Beers data
brew = read.csv('./data/Breweries.csv',header = TRUE) # Import Breweries data
map = read.csv('./data/us-zip-code-latitude-and-longitude.csv',header = TRUE,sep=";")  # Import Zipcode USA Coordinates

beers <- beers %>% filter(!is.na(ABV))
beers <- beers %>% filter(!is.na(IBU))

fluidPage(
  
  # App title ----
  titlePanel("Data Selection"),
  
  # Sidebar layout with input and output definitions ----
  sidebarLayout(
    
    # Sidebar panel for inputs ----
    sidebarPanel(
      
      # Input: Text for providing a caption ----
      # Note: Changes made to the caption in the textInput control
      # are updated in the output area immediately as you type
      textInput(inputId = "caption",
                label = "Caption:",
                value = "Data Summary"),
      
      # Input: Selector for choosing dataset ----
      selectInput(inputId = "dataset",
                  label = "Choose a dataset:",
                  choices = c("Beer", "Breweries")),
      
      # Input: Numeric entry for number of obs to view ----
      numericInput(inputId = "obs",
                   label = "Number of observations to view:",
                   value = 10)
      
    ),
    
    # Main panel for displaying outputs ----
    mainPanel(
      
      # Output: Formatted text for caption ----
      h3(textOutput("caption", container = span)),
      
      # Output: Verbatim text for data summary ----
      verbatimTextOutput("summary"),
      
      # Output: HTML table with requested number of observations ----
      tableOutput("view")
      
    )
  )
)

# Define server logic to summarize and view selected dataset ----

  
  # Return the requested dataset ----
  # By declaring datasetInput as a reactive expression we ensure
  # that:
  #
  # 1. It is only called when the inputs it depends on changes
  # 2. The computation and result are shared by all the callers,
  #    i.e. it only executes a single time
  datasetInput <- reactive({
    switch(input$dataset,
           "Beer" = beers,
           "Breweries" = brew)
  })
  
  # Create caption ----
  # The output$caption is computed based on a reactive expression
  # that returns input$caption. When the user changes the
  # "caption" field:
  #
  # 1. This function is automatically called to recompute the output
  # 2. New caption is pushed back to the browser for re-display
  #
  # Note that because the data-oriented reactive expressions
  # below don't depend on input$caption, those expressions are
  # NOT called when input$caption changes
  renderText({
    input$caption
  })
  
  # Generate a summary of the dataset ----
  # The output$summary depends on the datasetInput reactive
  # expression, so will be re-executed whenever datasetInput is
  # invalidated, i.e. whenever the input$dataset changes
  renderPrint({
    dataset <- datasetInput()
    summary(dataset)
  })
  
  # Show the first "n" observations ----
  # The output$view depends on both the databaseInput reactive
  # expression and input$obs, so it will be re-executed whenever
  # input$dataset or input$obs is changed
  renderTable({
    head(datasetInput(), n = input$obs)
  })
  
```


```{r tabsets, echo=FALSE}
mergeData = inner_join(brew,beers, by = c("Brew_ID" = "Brewery_id"))
mergeData <- dplyr::rename(mergeData, brewName = Name.x)
mergeData <- dplyr::rename(mergeData, beerName = Name.y)


fluidPage(
  
  # Application title
  titlePanel("Histogram of IBU"),
  
  # Sidebar with a slider input for number of bins 
  sidebarLayout(
    sidebarPanel(
      sliderInput("bins",
                  "Number of bins:",
                  min = 1,
                  max = 50,
                  value = 30)
    ),
    
    # Show a plot of the generated distribution
    mainPanel(
      plotOutput("distPlot")
    )
  )
)

# Define server logic required to draw a histogram

renderPlot({
    # generate bins based on input$bins from ui.R
    IBU_Content   <- mergeData$IBU
    bins <- seq(min(IBU_Content), max(IBU_Content), length.out = input$bins + 1)
    
    # draw the histogram with the specified number of bins
    hist(IBU_Content, breaks = bins, col = 'darkgray', border = 'white')
  })



```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.




```{r tabsets0, echo=FALSE}
shiny::shinyAppDir(
"~/datascience/DS6306/html/build/gobble/",
  options = list(
    width = "100%", height = 550
  )
)
```


```{r tabsets1, echo=FALSE}
shiny::shinyAppDir(
"~/datascience/DS6306/html/build/gobble1/",
  options = list(
    width = "100%", height = 550
  )
)

```


```{r tabsets2, echo=FALSE}
shiny::shinyAppDir(
"~/datascience/DS6306/html/build/gobble2/",
  options = list(
    width = "100%", height = 550
  )
)

```



```{r tabsets3, echo=FALSE}
shiny::shinyAppDir(
"~/datascience/DS6306/html/build/gobble3/",
  options = list(
    width = "100%", height = 550
  )
)
```

## ABV Filter By State and City

```{r tabsets4, echo=FALSE}
shiny::shinyAppDir(
"~/datascience/DS6306/html/build/gobble4/",
  options = list(
    width = "100%", height = 550
  )
)

```

## IBU Filter By State and City

```{r tabsets5, echo=FALSE}
shiny::shinyAppDir(
"~/datascience/DS6306/html/build/gobble5/",
  options = list(
    width = "100%", height = 550
  )
)

```

## ABV vs IBU with regression model line

```{r tabsets6, echo=FALSE}
shiny::shinyAppDir(
"~/datascience/DS6306/html/build/gobble6/",
  options = list(
    width = "100%", height = 550
  )
)

```

## ABV vs IBU with regression model line Per State

```{r tabsets7, echo=FALSE}
shiny::shinyAppDir(
"~/datascience/DS6306/html/build/gobble7/",
  options = list(
    width = "100%", height = 550
  )
)